---
title: "gg_hist_qq_boot_and_gg_scatter_boot"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{gg_hist_qq_boot_and_gg_scatter_boot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(semboottools)
library(lavaan)
```

## Overview

This vignette demonstrates two ggplot2-based utilities for visualizing bootstrap estimates stored/returned by **semboottools**:

- `gg_hist_qq_boot()`: modular histogram/density with optional CI, mean/boot-mean lines, SD arrow, and a side-by-side QQ plot.  
- `gg_scatter_boot()`: a scatterplot matrix (via **GGally**) for multiple parameters’ bootstrap draws.  

Compared to base plots, these functions are **modern** (*ggplot2*) and **modular** (optional layers), and can **return the ggplot objects** for further customization.  

**Dependencies:** Requires `ggplot2` (and `GGally` for the scatterplot matrix).  
Optional: `patchwork` to arrange histogram and QQ plots side-by-side.


## Example

```{r}
library(lavaan)

# Simulate data
set.seed(1234)
n <- 200
x <- runif(n) - 0.5
m <- 0.4 * x + rnorm(n)
y <- 0.3 * m + rnorm(n)
dat <- data.frame(x, m, y)

# Specify model
model <- '
  m ~ a * x
  y ~ b * m + cp * x
  ab := a * b
'

# Fit model
fit0 <- sem(model, data = dat, fixed.x = FALSE)

# Store bootstrap draws
fit2 <- store_boot(
  fit0,
  R = 5000,
  iseed = 2345)
```

### Basic usage: default settings
```{r}
gg_hist_qq_boot(fit2, param = "ab", standardized = FALSE)
gg_scatter_boot(fit2, c("ab", "a", "b"), standardized = FALSE)
```

```{r}
gg_hist_qq_boot(fit2, param = "ab", standardized = TRUE)
gg_scatter_boot(fit2, c("ab", "a", "b"), standardized = TRUE)
```


