---
title: "hist_qq_boot() and  scatter_boot()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hist_qq_boot() and  scatter_boot()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
devtools::load_all()
library(semboottools)
library(lavaan)
```

## Function Syntax
```{r eval = FALSE}
hist_qq_boot <- function(object,
                      param,
                      standardized = NULL,
                      nclass = NULL,
                      hist_color = "#5DADE233",
                      hist_linewidth = 1.5,
                      hist_border_color = "#1B4F72",
                      density_line_type = "solid",
                      density_line_color = "#8B0000CC",
                      density_line_linewidth = 2,
                      est_line_color = "#154360",
                      est_line_type = "dashed",
                      est_line_linewidth = 2,
                      qq_dot_pch = 21,
                      qq_dot_color = "#1B4F72",
                      qq_dot_fill = "#5DADE233",
                      qq_dot_size = 1.3,
                      qq_line_color = "#8B0000CC",
                      qq_line_linewidth = 2.1,
                      qq_line_linetype = "solid"
                      )

scatter_boot <- function(object,
                         params,
                         standardized = NULL,
                         main = "Bootstrap Estimates",
                         )
```

## Arguments

### hist_qq_boot

| Argument               | Description                                                                                                                                                                  |
|-----------------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| `object`               | The fitted `lavaan` model or the result from `standardizedSolution_boot()` / `parameterEstimates_boot()`. Bootstrap estimates must already be stored in the object.           |
| `param`                | The name of the parameter you want to plot (as shown in `coef()` output).                                                                                                     |
| `standardized`         | Set to `TRUE` if you want to plot standardized estimates, `FALSE` for unstandardized. If using the output from `standardizedSolution_boot()`, this is set automatically.      |
| `nclass`               | Number of bars (bins) in the histogram. Optional.                                                                                                                             |
| `hist_color`           | Color of the histogram bars.                                                                                                                                                 |
| `hist_linewidth`       | Width of the histogram bar borders.                                                                                                                                          |
| `density_line_type`    | Style of the density curve line (e.g., `"solid"`, `"dashed"`).                                                                                                                |
| `density_line_color`   | Color of the density curve.                                                                                                                                                  |
| `density_line_linewidth`| Width of the density curve line.                                                                                                                                            |
| `est_line_type`        | Style of the vertical line showing the parameter's point estimate (e.g., `"dotted"`).                                                                                         |
| `est_line_color`       | Color of the vertical line showing the point estimate.                                                                                                                       |
| `est_line_linewidth`   | Width of the vertical line showing the point estimate.                                                                                                                       |
| `qq_dot_size`          | Size of the dots in the QQ plot.                                                                                                                                             |
| `qq_dot_color`         | Color of the dots in the QQ plot.                                                                                                                                            |
| `qq_dot_pch`           | Shape of the dots in the QQ plot (numeric).                                                                                                                                  |
| `qq_line_linewidth`    | Width of the diagonal line in the QQ plot.                                                                                                                                   |
| `qq_line_color`        | Color of the diagonal line in the QQ plot.                                                                                                                                   |
| `qq_line_linetype`     | Style of the diagonal line in the QQ plot (e.g., `"solid"`).                                                                                                                  |

### scatter_boot()

| Argument        | Description                                                                                                                                                                        |
|-----------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| `object`        | A fitted `lavaan` model, or the output from `standardizedSolution_boot()` / `parameterEstimates_boot()`. Make sure the bootstrap estimates are stored before calling this function. |
| `params`        | A character vector with **two or more** parameter names to include in the scatterplot matrix. The names should match those in `coef()` output.                                      |
| `standardized`  | Logical. Set to `TRUE` to plot standardized estimates, or `FALSE` for unstandardized ones. If using `standardizedSolution_boot()` output, this is handled automatically.            |
| `main`          | Title of the scatterplot matrix. Default is `"Bootstrap Estimates"`.                                                                                                    
| `...`           | Other optional arguments passed to [psych::pairs.panels()] to further customize the appearance of the scatterplot matrix (e.g., correlation method, grid lines, etc.).              |

## Example

```{r}
library(lavaan)

# Simulate data
set.seed(1234)
n <- 200
x <- runif(n) - 0.5
m <- 0.4 * x + rnorm(n)
y <- 0.3 * m + rnorm(n)
dat <- data.frame(x, m, y)

# Specify model
model <- '
  m ~ a * x
  y ~ b * m + cp * x
  ab := a * b
'

# Fit model
fit1 <- sem(model, data = dat, se = "boot", bootstrap = 1000)
fit2 <- sem(model, data = dat, fixed.x = FALSE)
```

### Basic usage: default settings
```{r, fig.width = 6, fig.height = 3,fig.align='center'}
fit1 <- store_boot(fit1)
hist_qq_boot(fit1, param = "ab", standardized = FALSE)

```

```{r}
scatter_boot(fit1, c("ab", "a", "b"), standardized = FALSE)
```

```{r, fig.width = 6, fig.height = 3, fig.align='center'}
fit2 <- store_boot(fit2)
hist_qq_boot(fit2, param = "ab", standardized = TRUE)
```

```{r}
scatter_boot(fit2, c("a", "b", "ab"), standardized = TRUE)
```
